Structural controllability of ecological networks

### 2018-06-26 paper/manuscript.Rmd
minor tweak to caption of Table 1

dplyr::bind_rows(cc_table) %>%
  dplyr::select(-logLik, - AICc) %>%
  set_names(., pretty_term_names(colnames(.), "short")) %>%
  knitr::kable("latex", 
               # col.names = pretty_term_names(colnames(.), "short"),
               booktabs = T,
               caption = "Selection table of the generalised linear models of control capacity, $\\phi$. Only models with a weight larger or equal to 0.01 are shown.", 
               row.names = F, 
               digits = 2, 
               escape = F) %>%
  kableExtra::add_header_above(c("model terms" = 10, " " = 3), escape = F) %>%
  kableExtra::kable_styling(font_size = 8) %>%
  # kableExtra::group_rows("control capacity models", 1, nrow(cc_table)) %>%
  # kableExtra::group_rows("superior probability models", nrow(cc_table) + 1, nrow(cc_table) + nrow(su_table)) %>%
  kableExtra::footnote(general = "intercept (int), degree ($k$), trophic level ($l$), asymmetry ($a$), contribution to nestedness ($n$), visitation strength ($s$).", 
                       general_title = "Terms: ", 
                       footnote_as_chunk = TRUE, 
                       threeparttable = TRUE, 
                       escape = F)
```

>>>>

dplyr::bind_rows(cc_table) %>%
  dplyr::select(-logLik, - AICc) %>%
  set_names(., pretty_term_names(colnames(.), "short")) %>%
  knitr::kable("latex", 
               # col.names = pretty_term_names(colnames(.), "short"),
               booktabs = T,
               caption = "Selection table of the binomial generalised linear models of species control capacity, $\\phi$. Only models with a weight larger or equal to 0.01 are shown.", 
               row.names = F, 
               digits = 2, 
               escape = F) %>%
  kableExtra::add_header_above(c("model terms" = 10, " " = 3), escape = F) %>%
  kableExtra::kable_styling(font_size = 8) %>%
  # kableExtra::group_rows("control capacity models", 1, nrow(cc_table)) %>%
  # kableExtra::group_rows("superior probability models", nrow(cc_table) + 1, nrow(cc_table) + nrow(su_table)) %>%
  kableExtra::footnote(general = "intercept (int), degree ($k$), trophic level ($l$), asymmetry ($a$), contribution to nestedness ($n$), visitation strength ($s$).", 
                       general_title = "Terms: ", 
                       footnote_as_chunk = TRUE, 
                       threeparttable = TRUE, 
                       escape = F)
```
